Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-02 Experiments.tex
Fixing according Shantenu's comments

In this experiment  we run as many AthenaMP instances (hereafter referred to
as tasks)  as the number of nodes controlled by the pilot. Each AthenaMP
simulates 100 events, requiring $\sim 70$ minutes on average. \jhanote{Please
convert all measurements into seconds!}

Tasks do not  wait within the NGE Agent's queue since  one node  is available
to each AthenaMP instance.  Overheads in task execution are consequence
primarily of the three other factors: (i) the  initial bootstrapping of the
pilot on the nodes; (ii) the UnitManager's dispatching of  units (tasks) to
the agent; and (iii) time for the agent to spawn all the tasks on the nodes.
\jhanote{"spawn" is the right word here. The agent does not spawn tasks. These
are predefined. I would say "initialize" maybe? Something better?}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: Average duration of a
    single AthenaMP execution, average pilot duration and pilot's overhead as a function of different pilot sizes. \jhanote{Caption should be in consistent order as the bars in the figure. Ideally pilot first then AthenMP.}}
\label{fig:weakScal1a}
\end{figure}

% Firstly, w
We % can
observe that, despite some fluctuations due to external factors
% \footnote{such as the
(e.g., Titan's shared filesystem and the shared database used by the NGE), the
average execution time of AthenaMP % oscillates
ranges between 4200 and 4800 seconds. % Secondly, w
We % can
also observe that in all the cases the gap between AthenaMP execution times and
the pilot durations is minimal, although it slightly increases with the pilot
size. % By observing NGE's overhead, w
We % can
notice that NGE's overhead does not grow linearly with the number of units.
\jhanote{It does grow linearly with units! What am I missing??}

@@

\mtnote{we dowe need to keep it below 2 hours?}\aanote{You are right. It was misleadind. I Changed. Check if you like it.}

In these experiments, we run five AthenaMP instances per node.  As these
experiments are designed to investigate the overhead generated by the
scheduling and bootstrap of AthenaMP instances, we reduced the number of
events simulated by each AthenaMP task to sixteen in such a way that the
running time of each AthenaMP is, on average, $\sim 20$ minutes. This
experiment design choice does not affect the  objectives or accuracy of the
experiments, but allows us to scale experiments to large node counts by being
conservative with allocation.

@@

We ran
% different
pilots
% sizes, i.e. :
with 256, 512, 1024 and 2048 worker nodes and
%. For all of them, the walltime was
3\mtnote{2?} hours walltime. Figure~\ref{fig:weakScal2a} depicts the average
pilot duration, the average execution time of five sequential
generations\mtnote{generations?}\aanote{Changed} of AthenaMP, and the corresponding overhead. We
% can
observe that the difference between the two durations is more marked than in the
previous experiments \mtnote{mostly due to the increased overhead?}\aanote{Well, I guess that's plain.}. Despite this, we notice that the growth of the overhead is consistent with the increment of the number of tasks per node for pilots with 256, 512 and 1024 worker nodes, and much less than linear for the pilot with 2048 worker nodes \aanote{Although that histogram is not trustworty because it is generate with only two runs.}

>>>>

In this experiment  we run as many AthenaMP instances (hereafter referred to
as tasks)  as the number of nodes controlled by the pilot. Each AthenaMP
simulates 100 events, requiring $\sim 4200$ seconds on average. \jhanote{Please
convert all measurements into seconds!}\aanote{Done}

Tasks do not  wait within the NGE Agent's queue since  one node  is available
to each AthenaMP instance.  Overheads in task execution are consequence
primarily of the three other factors: (i) the  initial bootstrapping of the
pilot on the nodes; (ii) the UnitManager's dispatching of  units (tasks) to
the agent; and (iii) time for the agent to initialize all the tasks on the nodes.
\jhanote{"spawn" is the right word here. The agent does not spawn tasks. These
are predefined. I would say "initialize" maybe? Something better?}\aanote{Done. I put initialize, maybe bootstrap would be better?}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: average pilot duration, average  duration of a
    single AthenaMP execution, and pilot's overhead as a function of different pilot sizes. \jhanote{Caption should be in consistent order as the bars in the figure. Ideally pilot first then AthenMP.}}
\label{fig:weakScal1a}
\end{figure}

% Firstly, w
We % can
observe that, despite some fluctuations due to external factors
% \footnote{such as the
(e.g., Titan's shared filesystem and the shared database used by the NGE), the
average execution time of AthenaMP % oscillates
ranges between 4200 and 4800 seconds. % Secondly, w
We % can
also observe that in all the cases the gap between AthenaMP execution times and
the pilot durations is minimal, although it slightly increases with the pilot
size. % By observing NGE's overhead, w
We % can
notice that NGE's overhead does grow linearly with the number of units.
\jhanote{It does grow linearly with units! What am I missing??}\aanote{Corrected. I think that ``not'' came from a previous version of the sentence. }

@@

\mtnote{we dowe need to keep it below 2 hours?}\aanote{You are right. It was misleading. I Changed. Check if you like it.}

In these experiments, we run five AthenaMP instances per node.  As these
experiments are designed to investigate the overhead generated by the
scheduling and bootstrap of AthenaMP instances, we reduced the number of
events simulated by each AthenaMP task to sixteen in such a way that the
running time of each AthenaMP is, on average, $\sim 1200$ seconds. This
experiment design choice does not affect the  objectives or accuracy of the
experiments, but allows us to scale experiments to large node counts by being
conservative with allocation.

@@

We ran
% different
pilots
% sizes, i.e. :
with 256, 512, 1024 and 2048 worker nodes and
%. For all of them, the walltime was
3\mtnote{2?} hours walltime. Figure~\ref{fig:weakScal2a} depicts the average
pilot duration, the average execution time of five sequential
generations\mtnote{generations?}\aanote{Changed} of AthenaMP, and the corresponding overhead. We
% can
observe that the difference between the two durations is more marked than in the
previous experiments \mtnote{mostly due to the increased overhead?}\aanote{Well, I guess that's plain.}. Despite this, we notice that the growth of the overhead is consistent with the increment of the number of tasks per node for pilots with 256, 512 and 1024 worker nodes, and less than linear for the pilot with 2048 worker nodes.
